### 2017-10-10 character_coding/CharacterEvolution.Rmd
changed index column sequence for depth PCAs

#Working directory
setwd("~/Dropbox/siphonophore_phylogeny_2017/character_coding")

@@

###Phylogenetic PCA for bathymetrics
```{r pPCA_depth, echo=F, fig.height=10, fig.width=19, message=F, warning=F}
phyl.pca(dpruned_tree, dpruned_data[,c(13,14,15,17,18)], mode="corr") %>% biplot

dpruned_data[,c(13,14,15,17,18)] %>% PCA(graph=F) -> Zpca
Zpca %>% fviz_screeplot(addlabels=T)
Zpca %>% fviz_contrib(choice="var", axes=1, sort.val="desc")
Zpca %>% fviz_pca_biplot( col.var="contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel = TRUE)

phyl.pca(dpruned_tree, dpruned_data[,c(13,14,15,17,18)], mode="corr") -> ppcaZ
prcomp( dpruned_data[,c(13,14,15,17,18)]) -> rpcaZ
rpcaZ$rotation = ppcaZ$L
rpcaZ$x = ppcaZ$S
rpcaZ$scale = TRUE

>>>>

#Working directory
#setwd("~/Dropbox/siphonophore_phylogeny_2017/character_coding")
setwd("character_coding")

@@

###Phylogenetic PCA for bathymetrics
```{r pPCA_depth, echo=F, fig.height=10, fig.width=19, message=F, warning=F}
phyl.pca(dpruned_tree, dpruned_data[,c(14,15,16,18,19)], mode="corr") %>% biplot

dpruned_data[,c(14,15,16,18,19)] %>% PCA(graph=F) -> Zpca
Zpca %>% fviz_screeplot(addlabels=T)
Zpca %>% fviz_contrib(choice="var", axes=1, sort.val="desc")
Zpca %>% fviz_pca_biplot( col.var="contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel = TRUE)

phyl.pca(dpruned_tree, dpruned_data[,c(14,15,16,18,19)], mode="corr") -> ppcaZ
prcomp( dpruned_data[,c(14,15,16,18,19)]) -> rpcaZ
rpcaZ$rotation = ppcaZ$L
rpcaZ$x = ppcaZ$S
rpcaZ$scale = TRUE

### 2017-10-10 manuscript.rmd
changed index column sequence for depth PCAs

Phylogenetic PCA for bathymetrics
```{r pPCA_depth, echo=F, fig.height=18, fig.width=18, message=F, warning=F}
phyl.pca(dpruned_tree, dpruned_data[,c(13,14,15,17,18)], mode="corr") %>% biplot

dpruned_data[,c(13,14,15,17,18)] %>% PCA(graph=F) -> Zpca
Zpca %>% fviz_screeplot(addlabels=T)
Zpca %>% fviz_contrib(choice="var", axes=1, sort.val="desc")
Zpca %>% fviz_pca_biplot( col.var="contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel = TRUE)

phyl.pca(dpruned_tree, dpruned_data[,c(13,14,15,17,18)], mode="corr") -> ppcaZ
prcomp( dpruned_data[,c(13,14,15,17,18)]) -> rpcaZ
rpcaZ$rotation = ppcaZ$L
rpcaZ$x = ppcaZ$S
rpcaZ$scale = TRUE

>>>>

Phylogenetic PCA for bathymetrics
```{r pPCA_depth, echo=F, fig.height=18, fig.width=18, message=F, warning=F}
phyl.pca(dpruned_tree, dpruned_data[,c(14,15,16,18,19)], mode="corr") %>% biplot

dpruned_data[,c(14,15,16,18,19)] %>% PCA(graph=F) -> Zpca
Zpca %>% fviz_screeplot(addlabels=T)
Zpca %>% fviz_contrib(choice="var", axes=1, sort.val="desc")
Zpca %>% fviz_pca_biplot( col.var="contrib", gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel = TRUE)

phyl.pca(dpruned_tree, dpruned_data[,c(14,15,16,18,19)], mode="corr") -> ppcaZ
prcomp( dpruned_data[,c(14,15,16,18,19)]) -> rpcaZ
rpcaZ$rotation = ppcaZ$L
rpcaZ$x = ppcaZ$S
rpcaZ$scale = TRUE
